<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{An R Markdown Vignette made with knitr}
-->

Finnish open government data toolkit for R
===========

This is an R package for Finnish open government data. New
contributions are [welcome!](http://louhos.github.com/contact.html).

This work is part of the [rOpenGov](http://ropengov.github.com)
project.


### Installing and loading the release version

For general users:

```{r install, eval=FALSE}
install.packages("sorvi")
library(sorvi)
```

### Installing and loading the development version

For developers:

```{r install2, eval=FALSE}
install.packages("devtools")
library(devtools)
install_github("sorvi", "ropengov")
library(sorvi)
```

Further installation and development instructions can be found at the
project [home page](http://louhos.github.com/sorvi). 


### Using the package

For further usage
examples, see [Louhos-blog](http://louhos.wordpress.com) and
[Datawiki](https://github.com/louhos/sorvi/wiki/Data).


### Licensing and Citations

This work can be freely used, modified and distributed under the 
[Two-clause FreeBSD license](http://en.wikipedia.org/wiki/BSD\_licenses).

Kindly cite the work, if appropriate, as 'Leo Lahti, Juuso Parkkinen
ja Joona Lehtomäki (2011). sorvi - suomalainen avoimen datan
työkalupakki. URL: http://louhos.wordpress.com)'. 

A full list of authors and contributors and the relevant contact
information is [here](http://louhos.github.com/contact). The main
admins are Leo Lahti, Juuso Parkkinen and Joona Lehtomäki.

More information of the project is available at the project [home
page](http://louhos.github.com/sorvi).


### Session info


This vignette was created with

```{r sessioninfo, message=FALSE, warning=FALSE}
sessionInfo()
```




